Figure 3 - ChIP

### 2024-07-15 ms_figure_3_chip.Rmd
rearrange Fig3 panels A,B and add new panel C with atf1 network with shiny-tunable coordinates

---
title: "Figure 3 - ChIP"
author: "Michael Stadler, Charlotte Soneson, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    genomefasta: "reference/Schizosaccharomyces_pombe.ASM294v2.dna.toplevel.fa"
    gtf: "reference/Schizosaccharomyces_pombe.ASM294v2.55.gtf"
    chiptrackfile: "data/genome_browser_tracks_chipseq.csv.gz"
    peakcsv: "data/fused_peaks_filtered.csv.gz"
    peakenr: "data/fused_peaks_filtered_enrichments.csv.gz"
    peakchipfile: "data/fused_peaks_filtered_counts-external_chip.csv.gz"
    dbdtxt: "data/TF_DBD_annotation.txt"
    motifrds: "data/motifs_annotated.rds"
    txcsv: "data/promoters-1kb_tes-1kb_annotated.csv.gz"
editor_options: 
    chunk_output_type: console
---

@@

```{r load-packages}
suppressPackageStartupMessages({
    library(circlize)
    library(ComplexHeatmap)
    library(grid)
    library(ggplot2)
    library(cowplot)
    library(Biostrings)
    library(BSgenome)
    library(GenomicRanges)
    library(rtracklayer)
    library(tibble)
    library(tidyr)
    library(tidygraph)
    library(universalmotif)
    library(parallel)
    library(colorspace)
    library(scattermore)
    library(ggupset)
    library(dplyr)
    library(viridisLite)
    library(SummarizedExperiment)
    library(S4Vectors)
    library(jsonlite)
    library(dendextend)
    library(kableExtra)
    library(forcats)
    library(igraph)
    library(ggraph)
})

@@

# for each region in `from`, calculate the distance to its nearest element in `to`
# if there are no element in `to` on the sequence of `from`, set distance to NA
calc_distance_to_nearest <- function(from, to) {
    stopifnot(exprs = {
        is(from, "GRanges")
        is(to, "GRanges")
    })
    tmp <- distanceToNearest(x = from, subject = to)
    d <- rep(NA, length(from))
    d[queryHits(tmp)] <- mcols(tmp)$distance
    return(d)
}
```

@@

We can also create the same heatmap, but without showing the TF promoters (rows)
that are not detected to be bound by any TF.

@@

# ... remove "Non-bound"
keep <- promtype[o] != "Non-bound\nTF promoters"
o <- o[keep]

# ... create main heatmap with annotations
hm6 <- Heatmap(mprom[o, oc], name = "hm6",
               col = circlize::colorRamp2(
                   breaks = seq(0, 2, length.out = 64),
                   colors = colorRampPalette(c(binary_heatmap_colors["FALSE"],
                                               main_colors[1],
                                               binary_heatmap_colors["TRUE"]))(64)),
               border = TRUE, border_gp = gpar(lwd = 0.5),
               cluster_rows = FALSE, show_row_dend = FALSE,
               cluster_columns = FALSE, show_column_dend = FALSE,
               row_split = droplevels(promtype[o]), row_title_gp = gpar(fontsize = fl),
               column_title = "TF ChIP-seq experiments",
               column_title_gp = gpar(fontsize = fl),
               show_row_names = FALSE, show_column_names = FALSE,
               right_annotation = rowLabels[o],
               use_raster = TRUE, show_heatmap_legend = FALSE,
               width = unit(w_peaksHm, "mm"), # heatmap body width
               height = unit(w_peaksHm * mean(keep), "mm"))

# manually create a legend
hm_legend <- Legend(labels = c("TFs binding to another TF promoter",
                               "TFs binding to their own promoter"),
                    title = " ", legend_gp = gpar(fill = c("#648FFF", "darkblue")))

@@

We construct a network in which the nodes represent TFs (shown in orange if
they were ChIP'ed in this study), and the edges represent detected binding
events. An edge starting at a TF `A` and ending at a TF `B` means that `A`
has been detected to bind the promoter of `B`.

We exclude `untagged`, and also the TFs `zas1` and `SPCC320.03` from the network.
`zas1` has `r sum(mprom["zas1", ] > 0)` bound TFs in its promoter, and 
`SPCC320.03` has `r sum(mprom["SPCC320.03", ] > 0)`, and if these would be
included, the network is hard to visualize.

@@

## Create graph
## ... select TFs
to_remove <- c("zas1", "SPCC320.03", "untagged")
sel_tfs <- setdiff(unique(rownames(mprom), colnames(mprom)), to_remove)
length(sel_tfs)

## ... create adjacency matrix (row: from TF, column: to TF promoter)
adjm <- matrix(0, nrow = length(sel_tfs), ncol = length(sel_tfs),
               dimnames = list(sel_tfs, sel_tfs))
adjm[setdiff(colnames(mprom), to_remove),
     setdiff(rownames(mprom), to_remove)] <- t(mprom[setdiff(rownames(mprom), to_remove),
                                                     setdiff(colnames(mprom), to_remove)] > 0)
gr <- graph_from_adjacency_matrix(adjm, mode = "directed")

## Remove singletons
comps <- components(gr)
too_small <- which(table(comps$membership) < 2)
keep <- V(gr)[!(comps$membership %in% too_small)]
gr <- induced_subgraph(gr, keep)

## Set attributes for vertices and edges
V(gr)$vertexclass <- ifelse(adjm[cbind(names(V(gr)), names(V(gr)))] > 0,
                            "Auto-regulated TF",
                            ifelse(names(V(gr)) %in% colnames(mprom),
                                   "ChIP'ed TF", "Other TF"))
V(gr)$shape <- "circle"
eL <- as_edgelist(gr)
recipr <- paste0(eL[,1], "-", eL[,2]) %in% paste0(eL[,2], "-", eL[,1]) & eL[,1] != eL[,2]
E(gr)$weight <- ifelse(recipr, 2, 1)
E(gr)$edgeclass <- ifelse(recipr, "Reciprocal", "Other")
E(gr)$color <- ifelse(recipr, gplots::col2hex(main_colors[3]), gplots::col2hex(na_color))

## Visualize
node_padding <- margin(.2, .2, .2, .2, "mm")
ggr <- ggraph(as_tbl_graph(gr), 
              layout = "igraph", algorithm = "fr") + 
    geom_edge_link(aes(start_cap = label_rect(node1.name, padding = node_padding),
                       end_cap = label_rect(node2.name, padding = node_padding),
                       color = edgeclass),
                   arrow = arrow(length = unit(2, 'mm'))) +
    geom_edge_loop(aes(start_cap = label_rect(node1.name, padding = node_padding),
                       end_cap = label_rect(node2.name, padding = node_padding)),
                   arrow = arrow(length = unit(2, 'mm'))) +  # Handle self-loops
    scale_edge_color_manual(values = c(Reciprocal = main_colors[3], 
                                       Other = gplots::col2hex(na_color)),
                            name = "") + 
    geom_node_point(size = 4, aes(fill = vertexclass, shape = vertexclass), 
                    color = "black", stroke = 0.1) + 
    scale_shape_manual(values = c("Other TF" = 21, "ChIP'ed TF" = 21, "Auto-regulated TF" = 22), name = "") +
    scale_fill_manual(values = c("Other TF" = gplots::col2hex(bg_color),
                                 "ChIP'ed TF" = gplots::col2hex(main_colors[5]),
                                 "Auto-regulated TF" = main_colors[5]),
                      name = "") + 
    geom_node_text(aes(label = name), size = 3.5, repel = TRUE, vjust = 1.8) + 
    theme_graph(base_family = "sans", plot_margin = margin(30, 10, 40, 10)) + 
    guides(fill = guide_legend(override.aes = list(size = 4, alpha = 1))) + 
    coord_cartesian(clip = "off") 
print(ggr)
```

@@

For clearer visualization, we create a sub-network including only the
connectsion to and from `Atf1`:

```{r make-network-atf1}
#| fig.width: 10
#| fig.height: 8

## Create graph
## ... identify TFs connected to atf1
to_keep <- rownames(adjm)[adjm["atf1", ] > 0 | adjm[, "atf1"] > 0]
length(to_keep)

## ... create adjacency matrix (row: from TF, column: to TF promoter)
adjm2 <- adjm[to_keep, to_keep]
gr2 <- graph_from_adjacency_matrix(adjm2, mode = "directed")

## Set attributes for vertices and edges
V(gr2)$vertexclass <- ifelse(adjm[cbind(names(V(gr2)), names(V(gr2)))] > 0,
                             "Auto-regulated TF",
                             ifelse(names(V(gr2)) %in% colnames(mprom),
                                    "ChIP'ed TF", "Other TF"))
V(gr2)$shape <- "circle"
eL <- as_edgelist(gr2)
recipr <- paste0(eL[,1], "-", eL[,2]) %in% paste0(eL[,2], "-", eL[,1]) & eL[,1] != eL[,2]
E(gr2)$weight <- ifelse(recipr, 2, 1)
E(gr2)$edgeclass <- ifelse(recipr, "Reciprocal", "Other")
E(gr2)$color <- ifelse(recipr, gplots::col2hex(main_colors[3]), gplots::col2hex(na_color))

## Visualize
node_padding <- margin(.2, .2, .2, .2, "mm")
ggr2 <- ggraph(as_tbl_graph(gr2), 
               layout = "igraph", algorithm = "fr") + 
    geom_edge_link(aes(start_cap = label_rect(node1.name, padding = node_padding),
                       end_cap = label_rect(node2.name, padding = node_padding),
                       color = edgeclass),
                   arrow = arrow(length = unit(2, 'mm'))) +
    geom_edge_loop(aes(start_cap = label_rect(node1.name, padding = node_padding),
                       end_cap = label_rect(node2.name, padding = node_padding)),
                   arrow = arrow(length = unit(2, 'mm'))) +  # Handle self-loops
    scale_edge_color_manual(values = c(Reciprocal = main_colors[3], 
                                       Other = gplots::col2hex(na_color)),
                            name = "") + 
    geom_node_point(size = 4, aes(fill = vertexclass, shape = vertexclass), 
                    color = "black", stroke = 0.1) + 
    scale_shape_manual(values = c("Other TF" = 21, "ChIP'ed TF" = 21, "Auto-regulated TF" = 22), name = "") +
    scale_fill_manual(values = c("Other TF" = gplots::col2hex(bg_color),
                                 "ChIP'ed TF" = gplots::col2hex(main_colors[5]),
                                 "Auto-regulated TF" = main_colors[5]),
                      name = "") + 
    geom_node_text(aes(label = name), size = 3.5, repel = TRUE, vjust = 1.8) + 
    theme_graph(base_family = "sans", plot_margin = margin(30, 10, 40, 10)) + 
    guides(fill = guide_legend(override.aes = list(size = 4, alpha = 1))) + 
    coord_cartesian(clip = "off") 
print(ggr2)
```

@@

```{r Fig3}
#| fig.width: 11.5
#| fig.height: 8.2
#| warning: false

cowplot::plot_grid(
    hm_prom_bound,
    cowplot::plot_grid(gnmtracks1, scale = 0.9),
    hm_motifs_small,
    cowplot::plot_grid(
        motifs_aligned, upsets_aligned,
        nrow = 1, rel_widths = c(1.25, 1)),
    nrow = 2,
    labels = c("A", "B", "C", "D"),
    align = "vh",
    axis = "b",
    rel_widths = c(1, 1),
    rel_heights = c(w_peaksHm + 10, w_peaksHm + 20)
)
```

>>>>

---
title: "Figure 3 - ChIP"
author: "Michael Stadler, Charlotte Soneson, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    genomefasta: "reference/Schizosaccharomyces_pombe.ASM294v2.dna.toplevel.fa"
    gtf: "reference/Schizosaccharomyces_pombe.ASM294v2.55.gtf"
    chiptrackfile: "data/genome_browser_tracks_chipseq.csv.gz"
    peakcsv: "data/fused_peaks_filtered.csv.gz"
    peakenr: "data/fused_peaks_filtered_enrichments.csv.gz"
    peakchipfile: "data/fused_peaks_filtered_counts-external_chip.csv.gz"
    dbdtxt: "data/TF_DBD_annotation.txt"
    motifrds: "data/motifs_annotated.rds"
    txcsv: "data/promoters-1kb_tes-1kb_annotated.csv.gz"
    coordsatf1: "data/visnetwork_coords_atf1.csv"
editor_options: 
    chunk_output_type: console
---

@@

```{r load-packages}
suppressPackageStartupMessages({
    library(circlize)
    library(ComplexHeatmap)
    library(grid)
    library(ggplot2)
    library(cowplot)
    library(Biostrings)
    library(BSgenome)
    library(GenomicRanges)
    library(rtracklayer)
    library(tibble)
    library(tidyr)
    library(tidygraph)
    library(universalmotif)
    library(parallel)
    library(colorspace)
    library(scattermore)
    library(ggupset)
    library(dplyr)
    library(viridisLite)
    library(SummarizedExperiment)
    library(S4Vectors)
    library(jsonlite)
    library(dendextend)
    library(kableExtra)
    library(forcats)
    library(igraph)
    library(ggraph)
    library(visNetwork)
    library(shiny)
})

@@

# for each region in `from`, calculate the distance to its nearest element in `to`
# if there are no element in `to` on the sequence of `from`, set distance to NA
calc_distance_to_nearest <- function(from, to) {
    stopifnot(exprs = {
        is(from, "GRanges")
        is(to, "GRanges")
    })
    tmp <- distanceToNearest(x = from, subject = to)
    d <- rep(NA, length(from))
    d[queryHits(tmp)] <- mcols(tmp)$distance
    return(d)
}

# create a network (directed graph) from an adjacency matrix
createNetwork <- function(adjmatrix, chippedTFs = colnames(mprom), settings = "igraph") {
    # create igraph graph object
    gr <- graph_from_adjacency_matrix(adjmatrix, mode = "directed")

    # remove singletons
    comps <- components(gr)
    too_small <- which(table(comps$membership) < 2)
    keep <- V(gr)[!(comps$membership %in% too_small)]
    gr <- induced_subgraph(gr, keep)

    # set attributes for vertices
    V(gr)$vertexclass <- ifelse(adjmatrix[cbind(names(V(gr)), names(V(gr)))] > 0,
                                "Auto-regulated TF",
                                ifelse(names(V(gr)) %in% chippedTFs,
                                       "ChIP'ed TF", "Other TF"))
    if (settings == "visNetwork") {
        V(gr)$shape <- "triangle"
        V(gr)$size <- 15
        V(gr)$label.cex = 1.0
    } else if (settings == "igraph") {
        V(gr)$shape <- "circle"
    } else {
        stop("Unknown 'settings' parameter")
    }

    # highlight edges for reciprocal interactions
    eL <- as_edgelist(gr)
    recipr <- paste0(eL[,1], "-", eL[,2]) %in% paste0(eL[,2], "-", eL[,1]) & eL[,1] != eL[,2]
    E(gr)$weight <- ifelse(recipr, 2, 1)
    E(gr)$edgeclass <- ifelse(recipr, "Reciprocal", "Other")
    E(gr)$color <- ifelse(recipr, gplots::col2hex(main_colors[3]), gplots::col2hex(na_color))

    # return object
    return(gr)
}
```

@@

We can also create the same heatmap, but without showing TF promoters (rows)
from the group "Non-bound TF promoters".

@@

# ... remove "Non-bound"
keep <- promtype[o] != "Non-bound\nTF promoters"
o2 <- o[keep]

# ... create main heatmap with annotations
hm6 <- Heatmap(mprom[o2, oc], name = "hm6",
               col = circlize::colorRamp2(
                   breaks = seq(0, 2, length.out = 64),
                   colors = colorRampPalette(c(binary_heatmap_colors["FALSE"],
                                               main_colors[1],
                                               binary_heatmap_colors["TRUE"]))(64)),
               border = TRUE, border_gp = gpar(lwd = 0.5),
               cluster_rows = FALSE, show_row_dend = FALSE,
               cluster_columns = FALSE, show_column_dend = FALSE,
               row_split = droplevels(promtype[o2]), row_title_gp = gpar(fontsize = fl),
               column_title = "TF ChIP-seq experiments",
               column_title_gp = gpar(fontsize = fl),
               show_row_names = FALSE, show_column_names = FALSE,
               right_annotation = rowLabels[o2],
               use_raster = TRUE, show_heatmap_legend = FALSE,
               width = unit(w_peaksHm, "mm"), # heatmap body width
               height = unit(w_peaksHm * mean(keep), "mm"))

# manually create a legend
hm_legend <- Legend(labels = c("TFs binding to another TF promoter",
                               "TFs binding to their own promoter"),
                    title = " ",
                    legend_gp = gpar(fill = c(main_colors[1],
                                              binary_heatmap_colors["TRUE"])))

@@

We construct a network in which the nodes represent TFs (the ones that were
ChIP'ed in this study are indicated by color), and the edges represent detected
binding events. An edge starting at a TF `A` and ending at a TF `B` means that
`A` targets the promoter of `B`.

We exclude the `untagged` experiment, TFs without targets and for the overall
network also the TFs `zas1` and `SPCC320.03`. `zas1` has
`r sum(mprom["zas1", ] > 0)` bound TFs in its promoter, and `SPCC320.03` has
`r sum(mprom["SPCC320.03", ] > 0)`, and if these were included, the network
would be hard to clearly visualize.

@@

## Create graph
## ... select TFs
to_remove <- c("zas1", "SPCC320.03", "untagged")
sel_tfs <- setdiff(unique(rownames(mprom), colnames(mprom)), to_remove)
cat("Number of TFs in network:", length(sel_tfs), "\n")

## ... create adjacency matrix (row: from TF, column: to TF promoter)
adjm <- matrix(0, nrow = length(sel_tfs), ncol = length(sel_tfs),
               dimnames = list(sel_tfs, sel_tfs))
adjm[setdiff(colnames(mprom), to_remove),
     setdiff(rownames(mprom), to_remove)] <- t(mprom[setdiff(rownames(mprom), to_remove),
                                                     setdiff(colnames(mprom), to_remove)] > 0)
gr <- createNetwork(adjm)

## Visualize
set.seed(123)
node_padding <- margin(.2, .2, .2, .2, "mm")
ggr <- ggraph(as_tbl_graph(gr), 
              layout = "igraph", algorithm = "fr") + 
    geom_edge_link(aes(start_cap = label_rect(node1.name, padding = node_padding),
                       end_cap = label_rect(node2.name, padding = node_padding),
                       color = edgeclass),
                   arrow = arrow(length = unit(2, 'mm'))) +
    geom_edge_loop(aes(start_cap = label_rect(node1.name, padding = node_padding),
                       end_cap = label_rect(node2.name, padding = node_padding)),
                   arrow = arrow(length = unit(2, 'mm'))) +  # Handle self-loops
    scale_edge_color_manual(values = c(Reciprocal = main_colors[3], 
                                       Other = gplots::col2hex(na_color)),
                            name = "") + 
    geom_node_point(size = 4, aes(fill = vertexclass, shape = vertexclass), 
                    color = "black", stroke = 0.1) + 
    scale_shape_manual(values = c("Other TF" = 21, "ChIP'ed TF" = 21,
                                  "Auto-regulated TF" = 22), name = "") +
    scale_fill_manual(values = c("Other TF" = gplots::col2hex(bg_color),
                                 "ChIP'ed TF" = gplots::col2hex(main_colors[1]),
                                 "Auto-regulated TF" = gplots::col2hex(binary_heatmap_colors["TRUE"])),
                      name = "") + 
    geom_node_text(aes(label = name), size = 3.5, repel = TRUE, vjust = 1.8) + 
    theme_graph(base_family = "sans", plot_margin = margin(30, 10, 40, 10)) + 
    guides(fill = guide_legend(override.aes = list(size = 4, alpha = 1))) + 
    coord_cartesian(clip = "off") 
print(ggr)
```

@@

For clearer visualization, we create a sub-network including only the
connections to and from `Atf1` (but now also including `zas1` and
`SPCC320.03`):

```{r make-network-atf1}
#| fig.width: 5.75
#| fig.height: 6.8

## Create graph
## ... select TFs
to_remove <- c("untagged")
sel_tfs <- setdiff(unique(rownames(mprom), colnames(mprom)), to_remove)

## ... create adjacency matrix (row: from TF, column: to TF promoter)
adjm <- matrix(0, nrow = length(sel_tfs), ncol = length(sel_tfs),
               dimnames = list(sel_tfs, sel_tfs))
adjm[setdiff(colnames(mprom), to_remove),
     setdiff(rownames(mprom), to_remove)] <- t(mprom[setdiff(rownames(mprom), to_remove),
                                                     setdiff(colnames(mprom), to_remove)] > 0)
## ... identify TFs connected to atf1
to_keep <- rownames(adjm)[adjm["atf1", ] > 0 | adjm[, "atf1"] > 0]
cat("Number of TFs in network:", length(to_keep), "\n")

## ... create adjacency matrix (row: from TF, column: to TF promoter)
adjm2 <- adjm[to_keep, to_keep]
gr2 <- createNetwork(adjm2)

## Visualize
if (file.exists(params$coordsatf1)) {
    # create graph with manually optimized coordinates
    coordsAtf1 <- read.csv(params$coordsatf1)
    coordsAtf1$y <- -coordsAtf1$y

    ggr2 <- ggraph(as_tbl_graph(gr2), 
                   layout = as.matrix(coordsAtf1[, c("x", "y")]))
} else {
    # create graph using automated layout
    set.seed(234)
    ggr2 <- ggraph(as_tbl_graph(gr2), 
                   layout = "igraph", algorithm = "fr")

node_padding <- margin(.2, .2, .2, .2, "mm")
ggr2 <- ggr2 +
    geom_edge_link(aes(start_cap = label_rect(node1.name, padding = node_padding),
                       end_cap = label_rect(node2.name, padding = node_padding),
                       color = edgeclass),
                   arrow = arrow(length = unit(2, 'mm'))) +
    geom_edge_loop(aes(start_cap = label_rect(node1.name, padding = node_padding),
                       end_cap = label_rect(node2.name, padding = node_padding)),
                   arrow = arrow(length = unit(2, 'mm'))) +  # Handle self-loops
    scale_edge_color_manual(values = c(Reciprocal = main_colors[3], 
                                       Other = gplots::col2hex(na_color)),
                            name = "") + 
    geom_node_point(size = 4, aes(fill = vertexclass, shape = vertexclass), 
                    color = "black", stroke = 0.1) + 
    scale_shape_manual(values = c("Other TF" = 21, "ChIP'ed TF" = 21,
                                  "Auto-regulated TF" = 22), name = "") +
    scale_fill_manual(values = c("Other TF" = gplots::col2hex(bg_color),
                                 "ChIP'ed TF" = gplots::col2hex(main_colors[1]),
                                 "Auto-regulated TF" = gplots::col2hex(binary_heatmap_colors["TRUE"])),
                      name = "") + 
    geom_node_text(aes(label = name), size = 3.5, repel = TRUE, vjust = 1.8) + 
    theme_graph(base_family = "sans", plot_margin = margin(30, 10, 40, 10)) +
    theme(legend.position = "bottom") +
    guides(fill = guide_legend(override.aes = list(size = 4, alpha = 1))) + 
    coord_cartesian(clip = "off")

print(ggr2)
```

Below here is code that can be run manually and was used to manually
optimize the network display and export a csv file with node coordinates
(`r params$coordsatf1`):

```{r}
#| echo: false
#| eval: false

## Code for shiny app to generate coordinate csv file
shinyAppThresholds <- function(adjmatrix) {
    server <- function(input, output) {
        output$visnetwork <- renderVisNetwork({
            gr <- createNetwork(adjmatrix, settings = "visNetwork")
            visNetwork::visIgraph(gr)
        })

        # Get position info
        observeEvent(input$store_position, {
            visNetworkProxy("visnetwork") |> visGetPositions()
        })

        output$coordinates <- renderPrint({
            nodes_positions()
        })

        ## Format positions
        nodes_positions <- reactive({
            positions <- input$visnetwork_positions
            if (!is.null(positions)){
                nodes_positions <- do.call("rbind", lapply(positions, function(x){data.frame(x = x$x, y = x$y)}))
                nodes_positions$id <- names(positions)
                nodes_positions
            } else {
                NULL
            }
        })

        output$downloadCsv <- shiny::downloadHandler(
            filename = function() {
                "visnetwork_coords_atf1.csv"
            },
            content = function(file) {
                utils::write.table(nodes_positions(), file,
                                   row.names = FALSE, sep = ",",
                                   quote = FALSE)
            }
        )
    }

    ui <- fluidPage(
        visNetworkOutput("visnetwork", width = "100%", height = "1000px"),
        verbatimTextOutput("coordinates"),
        actionButton("store_position", "Store positions"),
        downloadButton("downloadCsv", "Download")
    )

    shinyApp(ui = ui, server = server)
}
shiny::runApp(shinyAppThresholds(adjm2))
```

@@

```{r Fig3}
#| fig.width: 11.5
#| fig.height: 11.1
#| warning: false

cowplot::plot_grid(
    cowplot::plot_grid(
        cowplot::plot_grid(
            hm_prom_bound,
            cowplot::plot_grid(gnmtracks1, scale = 0.9),
            nrow = 2,
            labels = c("A", "B"),
            rel_heights = c(0.75, 1)
        ),
        ggr2,
        nrow = 1,
        labels = c("", "C")
    ),
    cowplot::plot_grid(
        hm_motifs_small,
        cowplot::plot_grid(
            motifs_aligned, upsets_aligned,
            nrow = 1, rel_widths = c(1.25, 1)),
        nrow = 1,
        labels = c("D", "E")
    ),
    nrow = 2,
    labels = c("", ""),
    rel_heights = c(1.75 * (w_peaksHm + 10), w_peaksHm + 20)
)
```
